;<!-- TB3D 1.1.0.0.0.4 -->
<!-- Translated and corrected by Steve90k for fluency and ease of reading. Edited and proofed by Sword2012 for clarity, brevity, and consistency. 13 Mar 16 -->
[dead_reason]
1="a Springboard"
2="a Burner"
3="a Vortex"
4="a Whirligig"
5="an Elektra"
6="of shrapnel wounds... The poor bastard didn't even see it coming"
7="a wild Boar"
8="a Dog"
9="a Pseudodog"
10="a Bloodsucker"
11="some Rats"
12="It's not clear exactly what happened, but he's dead"
13="Looks like a radiation burn"
14="Ripped to shreds. Impossible to tell what kind of creature did it"
15="Shot in the head"
16="Had a hand ripped off in an anomaly. Died of blood loss"
17="His feet are a mess... Must have wandered into a Fruit Punch anomaly"
18="Shot in the chest"
19="Shot in the heart and head - a professional job. Most likely Mercenaries..."
20="A bloody smear on the concrete... Torn scraps of a shredded suit. Shattered PDA. Must have..."
21="Something must have been chasing him. He ran straight into an anomaly"
22="Bleeding from the nose and ears... Looks like radiation poisoning"
23="No visible wounds... An unexplained death"
24="Fell into a Burner anomaly. He must have dropped his PDA sometime before this, so I can't identify him"
25="Splattered all over the place... Typical Whirligig symptoms"
26="He didn't know what he was carrying in his backpack. Died from highly radioactive artefacts"
27="The suit is intact, but inside it's a mess. I don't know what the hell happened"
28="Marauders"
29="Ran into some Marauders... Didn't stand a chance"
30="Shot in the leg. Couldn't make it to safety. Died of blood loss"
31="Shot in the chest... put a hole right through him..."
32="Died from radiation poisoning... Should have been more careful"
33="The body's been chewed. Most likely by dogs... Poor bastard"
34="Gone without a trace... only his smouldering PDA found behind a boulder..."
35="His leg was ripped open, straight to the bone. Died from a massive blood haemorrhage"
36="Had a serious fracture. Couldn't move, and just lay there in pain for hours... Something must have found him..."
37="Shot at point-blank range. Must have been an ambush of Marauders... Filthy bastards!"
38="A shot in the back of the head"
39="I noticed a Bloodsucker lurching over the body. I killed it, and tried to help him, but he was already dead"
40="Strange burns over the whole body. Nothing like a Burner anomaly. More like a fucking flamethrower..."
41="A laceration on the chest. I don't know exactly what happened... Shit!"
42="I found a PDA next to the body. The recorder was still switched on. Playback is just hours of screaming. Horrible."
43="Found a body, all cut to pieces. Beside it was a small knife. What the hell happened here?"
44="A skeleton, wearing unscathed Stalker gear... WTF?"
45="Gnawed down to his bones by Rats..."
46="Both arms are broken and his neck's twisted. Who the hell did this?!"
47="A punctured skull, but no sign of a fight... Must have been a sniper"
48="Stitched up shoulder, but no bandages. Died from infection..."
49="came a pack of mad dogs."
50="came a pack of mad Pseudodogs."
51="a Controller appeared. Shit! Who's next?"
52="came a Controller."
53="Military Helicopter... Probably a raid..."
54="there was a wave of mutants. Barely got out alive! Others weren't so lucky."
55="attacked by mutants."
56="saw a mangled corpse there. Didn't try to investigate. Maybe there's an invisible anomaly close by..."
57="saw a rotting corpse nearby. Maybe there's a lair of Bloodsuckers near here..."
58="heard a terrible scream. Damn, I'm not going near there again!"
59="saw a bloody Stalker being dragged along the ground by a Bloodsucker. Fuck!!!"
60="saw a pack of dogs, dragging a Stalker into the bushes. It looked like he was still alive..."
61="was involved in a heated exchange with some Bandits. We killed them all. Fucking scumbags!"
62="ran into a Military patrol, and killed them all. Avoid that area if you can. There's sure to be a raid now!"
63="caught by a Military patrol. Had to shoot them all. I'd get out of here if I were you..."
64="a Snork killed a Stalker here. Shit, how many of those fuckers are there?"
65="There are many strange new anomalies around here. Go carefully, Stalker!"

[where_dead]
1="in the Cordon"
2="in the Cordon, near the tunnel with the Elektra"
3="in the Cordon, near the collapsed bridge"
4="in the Cordon, beside a rusty locomotive"
5="around the Cordon"
6="close to the Cordon"
7="before the Cordon"
8="far from the Cordon"
9="next to the Cordon"
10="near the Cordon"
11="at the Dump"
12="at the Dump, near the hangar"
13="around the Dump"
14="in the vicinity of the Dump"
15="before the Dump"
16="far from the Dump"
17="next to the Dump"
18="near the Dump"
19="in Agroprom"
20="in Agroprom, near the Institute"
21="around Agroprom"
22="in the vicinity of Agroprom"
23="before Agroprom"
24="far from Agroprom"
25="next to Agroprom"
26="near Agroprom"
27="in Yantar"
28="in Yantar, in the swamp"
29="in Yantar, at the factory"
30="around Yantar"
31="close to Yantar"
32="in front of Yantar"
33="near Yantar"
34="next to Yantar"
35="near Yantar"
36="in the Dark Valley"
37="around the Dark Valley"
38="close to the Dark Valley"
39="before the Dark Valley"
40="not far from the Dark Valley"
41="next to the Dark Valley"
42="near the Dark Valley"
43="at the Army Warehouses"
44="around the Army Warehouses"
45="close to the Army Warehouses"
46="before the Army Warehouses"
47="not far from the Army Warehouses"
48="next to the Army Warehouses"
49="near the Army Warehouses"
50="near the abandoned village"
51="near the deserted village"
52="in front of an abandoned village"
53="near the deserted village"
54="next to an abandoned village"
55="near the deserted village"
56="near the water tower, in the deserted village"
57="before the water tower in the village"
58="near the water tower, in the deserted village"
59="next to the old water tower"
60="near the water tower, in the village"
61="in the vicinity of the Bar"
62="before the Bar"
63="near the Bar"
64="near the Barrier"
65="near the Barrier"
66="before the Barrier"
67="near the Barrier"
68="next to the Barrier"
69="near the Barrier"
70="Rostock factory"
71="around the Rostok plant"
72="in the vicinity of the Rostok plant"
73="the Rostok plant"
74="not far from the Rostok plant"
75="next to the Rostok plant"
76="near the Rostok plant"
77="near the Duty base"
78="near the Duty checkpoint"
79="before the Duty checkpoint"
80="far from the Duty checkpoint"
81="next to the Duty checkpoint"
82="near the Duty checkpoint"
83="near the entrance to the Freedom base"
84="near the Freedom base"
85="next to the Freedom base"
86="near the Freedom base"
87="near the entrance to the Freedom base"
88="near the Freedom base"
89="in the ATP"
90="around the ATP"
91="in the vicinity of the ATP"
92="before the ATP"
93="far from the ATP"
94="next to the ATP"
95="near the ATP"
96="Farm"
97="near the farm"
98="in the vicinity of the farm"
99="in front of the farm"
100="not far from the farm"
101="next to the farm"
102="near the farm"
103="around the Scientists' camp"
104="near the Scientists' camp"
105="not far from the Scientists' camp"
106="next to the Scientists' camp"
107="near the entrance to the factory building in Yantar"
108="near the Yantar factory gates"
 