;<!-- TB3D 1.1.0.0.0.4 fixed \\n 83 places, \T and added callsigns, more callsigns, reordered, STAKERs, CyberSemtex -->
[news_uniq]
1="A couple of helicopters have just passed me. Coordinates enclosed. Stay safe. I don't know what their orders are."
2="We're continuing on the same bearing from the downed helicopter in the marshes. Nothing so far.\nShit, it's Duty!\nGo to the private channel, quickly!"
3="Waves of mutants coming from the northwest. See attached coordinates."
4="Waves of mutants, coming from the northern valley."
5="Waves of mutants heading east, presumably from the Dark Valley."
6="Mayday... A pack of dogs is coming straight for us. Exact coordinates given. Please help!"
7="If it's not mutants, it's bandits...\nPotap\nYes, we can guess..."
8="Just been rushed by a Pseudodog. Barely shot it in time!\nPotap\nWell done...
9="Mayday... A battle has broken out at the Agricultural Industry in the central complex!\n\nDuty\nAnyone doing the same as in here, be warned - you WILL be raided..."
10="Lukash, the Merc's been shot. On my way back.\nFreedom\nSwitch to the private channel, assholes!"
11="Two, Three, Seven, return to base and consolidate."
12="Marauders! We're being attacked! Help!\nNo one can help unless you attach your coordinates, idiot..."
13="We need access to the Internet. Should we make our way to the bar, where it's crowded, or go further to Sidorovich where it's more private?\nPotap\n Yes, the Bar will always be busy, but you can try the signallers at Duty. They also have access"
14="Has anyone figured out where those ALD weapons are?\nIt's probably a trap anyway..."
15="Crap...\nJust stepped in the biggest pile of boar shit ever!"
16="Where the hell am I?\nWhy is it so foggy out here?..."
17="I'm lost! I need help...\nIs anybody receiving this?\nAnybody...?"
18="So that explains it, but I don't know where the signal is coming from..."
19="In the Swamps, a Stalker named Kalmyak sells medical ointment. It really helps! Almost all my symptoms have gone. Much better than vodka!"
20="I'm going to try using emoticons more often :) ;) 8)... Communication scrambled...\nPotap\nIdiot blocked <:}"
21="A huge beast has turned up in the swamps. It's strong, and almost two metres tall. The Bandits near the church are covered in blood, and it's still alive... I gave them a bandage to share"
22="Just come from the Reconnoitred Earth. Saw the lake, nearby which was an Electric Chimera, grazing. I do NOT advise going there..."
23="Attention, all fighters! Bandits are trying to take over the ATP! This is our territory! Help us defend it!"
24="A group of five people are moving towards the Barrier. Looks like the Monolith. Take immediate action.\n\nBarrier\nUnderstood. Those fucking lunatics!"
25="Warning: In a small village in the Dark Valley, if you're offered a Gauss rifle for 800 roubles - don't believe it. It's a scam!"
26="What the hell? Just when you think everything's quietened down for the night, at 21.00 a shitload of fucking green-eyed zombies appear! I've heard of it, but never seen it happen here before!"
27="I've just heard that in the Red Forest there's a huge catfish living in the river. That would look great on the wall... "
28="You're not going to believe this, but a dead dog has just fallen out of the sky right next to me..."
29=" I've heard that an average of twenty people die each day in the Zone. I'm still here, but I see fewer and fewer people each day. My time must come soon..."
30="The client has accepted our price, and given us the details. Now we have a job to do..."
31="I heard you know about some lab - X-16? X-18? X-20? Tell me what you know, or you're dead..."
32="I heard that at the bar there's one guy, an informant. He sells transmutation Recipes for artefacts. Check it out..."
33="Fuck! It's impossible to get through Pripyat, what with those bastard helicopters shooting the shit out of anything that moves...!"
34="On the way to Limansk, I arrived at a construction site full of Monolith! Gettin' outa here quick before I'm seen!"
35="I drank some shit vodka. This is the second day I've been sat on a toilet, throwing up in a bucket..."
36="Nobody knows who the shooter is? One group is was very interested in finding out. They're offering a large reward"
37="There's a Snork here still alive after taking both barrels in the head. That's one tough mofo!"
38="Looks like the bastard offspring of two different mutants is living in the woods here"
39="Just killed a Chimera, but there's usually two in a nest"
40="Just saw a withered corpse, totally sucked dry. Indicates a den of Bloodsuckers close by"
41="Looking for a technician, preferably with experience of night vision devices. Dust-free working environment. Decent pay"
42="Found an exoskeleton in the ATP. Put in on and used it for ages, until I fell into a Springboard. Now, it's up in space somewhere..."
43="For Sale - Old exoskeleton. Sealing system is damaged, but otherwise in excellent condition"
44="Just fended off a major wave of mutants. Awaiting another one soon. Anyone who can help, come quickly"
45="The Duty warehouse has just received a batch of brand new FN-2000's. You need to get there quickly if you want to ste..., sorry, buy one"
46="Damn! The area around Yantar is full of zombies again! Neat job you did there, people!\nPotap\Carry on with the mission. We still need that information..."
47="Speak with the Bandits. They should know how to get through that area quietly..."
48="Attention all Stalkers who wish to clear their debts - go to a private channel for information on the upcoming mutant raid and other operations."
49="Went to Darkscape looking for Tweed\nGot chased out by a group of soldiers. No idea who they were..."
50="Is anybody out there?\nI need assistance. Anybody?\nWhere the hell am I?..."
51="FSS?\nWho the hell is that, anyway? Probably some jerk looking to cause trouble, no doubt!"
52="I had it!\nIt was awesome... but I lost it...\nIt just flew right outta my hand, and disappeared... Can't find it... Gotta find it, though..."
53="Did you hear about F1?\nEveryone's dead. It's far too hot to enter, and there are no clues as to what happened!"
54="Let's meet at the bar up north. Don't forget vodka for the guards at the gate."
55="Just tried to go to the old research station.\nWatch out - there's something definitely something wrong with that place. And extremely hostile!"
56="Top end military goods!\nAt the Black Market, for the next few days only"
57="Almost had it back!\nOn the rooftops, near the generators. But then it sliced up some Monolith bastards and disappeared again!"
58="Hey, did you hear?\nThe Duty commander in Rostok has lost his marbles. He actually sent out a team out to find a panda bear for him to take back to Moscow..."
59="Watch out at the Dead Marshes.\nOur whole village has been overrun by group of military assholes!"
60="Need a Stalker, preferably discreet for some... delicate work. Do not respond directly, but to the base"
61="Work available, to search for equipment. Payment per item found. Look for me in the Reconnoitered Earth, in the infirmary"
62="Looking for experienced Stalkers to raid for artefacts. Contact Petrenko"
63="In exchange for rare artefacts, I can now upload new firmware to your PDA. Even a satellite channel. Lanky. "
64="Heh-heh, even at my highest rates, the client is still desperate to do business with me!" 
65="Looking for a Stalker specialising in combination locks, with experience of raids to the north of the Zone."
66="I heard the Americans sent us a superhero. It'll be interesting to see him."
67="Do not go through the underground tunnels. They're full of mutants! Take the surface routes instead..."
68="Hey, they've got a shishka pipe in the Bar. Better get there quick before it gets raided!"
69="Everyone! Be careful staying in warehouses in the countryside. They're being burned down, and bodies piled up on posts!"
70="Stalkers! Sakharov pays well for exclusive items from raids! He needs someone to go to X-16. It's a risky area, full of bloodsuckers and zombies"
71="We need Stalkers for incursions into the Wild Territory. High rates of pay for good results. Kruglov.\nLabelled\nStalkers, if you want to keep your sanity, do not meet up with this Scientist. He's a nutcase!"
72="Join our ranks of experienced trackers. No entrance fees. Zahar"
73="Baldy\nGet a move on! If I see something coming I'll shoot..."
74="We need Stalkers with expertise of deep raids into the Zone. Payment commensurate with skill and results. If interested, respond privately to discuss a meeting"
75="Wolf, if you can talk safely, please come in..."
76="Stalkers, join Duty! Defend the planet from the new plague that is upon us..."
77="Spam\nMoskvin coffee - a really, truly, nasty Chinese-made coffee!"
78="Spam\nLost - weapons. If found, please return them to me at the old Stardusk wreck in Backwater. Come alone!"
79="Spam\nAntizombin - keeps the zombie in you at bay - even better than vodka!"
80="Spam\nMoskvin relieves you of constipation in exactly 30 seconds. No more, no less..."

[names]
1=Aleks1970
2=Oleg 
3=Oles 
4=Roma 
5=Ruslan 
6=Sasha 
7=GlowWorm 
8=Slava 
9=LaGator 
10=Jura 
11=Bogdan 
12=Veniamin 
13=Vitaly 
14=Vova 
15=Dima 
16=Ivan 
17=Freischutz 
18=Leche 
19=Andrei 
20=Sanya 
21=aZmoDen 
22=Wadi 
23=Vasyan 
24=Vasek 
25=Vityuha 
26=Vetal 
27=Vovan 
28=Zhorka 
29=Grishka 
30=Michal 
31=Grishko 
32=Dimona 
33=Lech 
34=Dimuha 
35=Mordeth 
36=Fimka 
37=CyberSemtex
38=Ireland 
39=Mitka 
40=Miha 
41=Mihas 
42=Kolyan 
43=Tolyan 
44=Pavluha 
45=Vesirott 
46=Stepka 
47=Stepuha 
48=Timoha 
49=Felka 
50=Yuras 
51=Yashka 
52=Andrjuxa 
53=Toha 
54=Arkady 
55=Temka 
56=Boryan 
57=Bodya 
58=Andrei 
59=Anton 
60=Oleg 
61=Roman 
62=Alexander 
63=Jammer 
64=Anatoly 
65=Yuri 
66=Bogdan 
67=Veniamin 
68=Vitaly 
69=Vladimir 
70=Dmitri 
71=Ivan 
72=Wolf_Urine 
73=Alexey 
74=Sane 
75=Sanya 
76=Arthur 
77=Yashka 
78=Yarick 
79=Yara 
80=Slava 
81=Zaldron 
82=Borka 
83=Bogdan 
84=Slawik 
85=Vadim 
86=Wadi 
87=Vadik 
88=Roller 
89=Valera 
90=Schurick 
91=Vase 
92=Vaska 
93=Vasko 
94=Vienna 
95=Whyte 
96=Vitka 
97=Vitalik 
98=Vlad 
99=Vova 
100=Vovka 
101=Leni 
102=Seva 
103=Sevco 
104=Gena 
105=Lord_Santa 
106=George 
107=Gosh 
108=Jore 
109=RemCNelly 
110=Gleb 
111=Grisha 
112=Alex 
113=Grishka 
114=Grishko 
115=Auzymindias 
116=Danilo 
117=Danko 
118=Denis 
119=Dima 
120=Dimka 
121=Dmytro 
122=Jack 
123=Leszka 
124=Zhenka 
125=Egor 
126=Egorka 
127=aZmoDen 
128=Vanya 
129=Vanka 
130=Igorek 
131=Ilya 
132=Kostya 
133=Kostik 
134=Death_Eagle 
135=Lew 
136=Leni 
137=Lenka 
138=Grimwald 
139=Matvey 
140=Mite 
141=Misha 
142=Mishka 
143=Nikita 
144=Nik 
145=Anton 
146=Kolya 
147=Oleg 
148=Pasha 
149=Pashka 
150=Petro 
151=Petey 
152=Petka 
153=Roma 
154=Romka 
155=Rostik 
156=Toshka 
157=Rus 
158=Sawa 
159=Semen 
160=Sema 
161=Serega 
162=Twilight2k 
163=Stepan 
164=dAVROs 
165=Pilgrim 
166=Timka 
167=Arte 
168=Fedora 
169=Fedya 
170=Fedka 
171=File 
172=Filka 
173=Edik 
174=Yurka 
175=Eureka 
176=Yurko 
177=Yash 
178=Sivy 
179=Mad 
180=Rotten 
181=TB3D 
182=spy 
183=Bizon 
184=Bober 
185=Bulldog 
186=Bic 
187=Sparrow 
188=Dyatel 
189=beast 
190=Serpent 
191=Hunchback 
192=Maximus86 
193=Karas 
194=Kenar 
195=Bedbug 
196=Bacon 
197=Los 
198=Patsyuk 
199=Udav 
200=Baton 
201=Bity 
202=Long 
203=Bespredel 
204=Bolt 
205=TrueB 
206=Tambourine 
207=Valet 
208=Vint 
209=Dynamite 
210=Kozyr 
211=Brass_knuckles 
212=Kosyak 
213=Dohly 
214=Crest 
215=Kryuk 
216=Lapot 
217=Lom 
218=Panadol 
219=Perot 
220=Piston 
221=Pyatak 
222=Reszka 
223=Death 
224=Dohodyaga 
225=Tochilo 
226=Ace 
227=Chekan 
228=Tempo 
229=Shiloh 
230=Szpala 
231=Hell 
232=Shuher 
233=fist 
234=Skull 
235=Dohlyak 
236=Barmaley 
237=Baty 
238=Undead 
239=Rambo 
240=Susanin 
241=Terminator 
242=Chapay 
243=Chingiz 
244=Banana 
245=Baton 
246=Inside 
247=Bata 
248=Bayan 
249=Bratan 
250=Gangrene 
251=Gluck 
252=Gradus 
253=Spirit 
254=Zvezdets 
255=Izgoj 
256=Brass_knuckles 
257=Zhzheny 
258=Kozyr 
259=Kosyak 
260=Lapot 
261=Leshy 
262=Mawr 
263=Nishtjak 
264=Oblom 
265=Erick 
266=Pepper 
267=Rashpil 
268=Zhirdyay 
269=Suhar 
270=Upyr 
271=Zhlob 
272=Bity 
273=Zhmot 
274=Jmour 
275=Izverg 
276=Caleca 
277=Kolotun 
278=Cosi 
279=Krivoy 
280=AQ 
281=Bald 
282=Lyuty 
283=Blatnoj 
284=Local 
285=Mutny 
286=Myaty 
287=Odnoglazy 
288=Padla 
289=Parasite 
290=Cool 
291=Swine 
292=churned 
293=Psycho 
294=Dino 
295=Rvany 
296=Rvach 
297=Blind 
298=Soplya 
299=Stilyaga 
300=Metropolitan 