;<!-- TB3D 1.0.9.9.9.9 fixed \\n 83 places, \T and added callsigns, more callsigns, reordered, STAKERs -->
[news_uniq]
1="A couple of helicopters have just passed me. Coordinates enclosed. Keep it safe, I do not know what their orders are."
2="We go on bearing the fallen helicopter in the marshes. No - none.\nIt is the duty\nin a private channel, crap!"
3="observed waves of mutants, is from the northwest, please see the attached coordinate."
4="observed waves of mutants, comes from the northern valley."
5="observed waves of mutants, goes to the east, presumably - from the dark valley."
6="May Day, a pack of dogs rushing straight at us, the exact coordinates included!"
7="Marauders, creatures ... \nPotap\nWe can guess."
8="Pseudodog rushed, barely shot!\nPotap\nWell done."
9="May Day... war have thrust on the Agricultural Industry in the Central Complex!\nIt is the duty\nand what you all itching to do it ... warned the same raid will be."
10="Lucas, Merck shot, go home.\nFreedom\nin the private channel, assholes!"
11="Two, three, seven, go home, meet."
12="Marauders clamped, help!\ncoordinates, enclose, wise guy."
13="We need access to the Internet. In the bar there, or to trudge Sidorovich?\nPotap\n Like the bartender is. Basically, you can try to go to the signalers - Duty - they just have access. "
14="Anyone ... figure out where those ALD weapons are?\n   probably a trap anyway... "
15="Crap... \nstepped in the biggest boar pile ever!"
16="where the hell am I... \nwhy is it so foggy out here..."
17="LOST!  need help.. \nis anybody receiving me, anybody..."
18="So ... explains once and for all - I would not say where the center of communication. "
19="The Swamps, a STALKER named Kalmyak, sells medical ointment ... It really helps. Sickness almost all were withdrawn, better than Vodka! "
20="I bet I'll write more of emoticons? Look: :), ;), 8)... Communication scrambled.\n\nPotap\nIdiot blocked >8) "
21="Ohrenet! In swamps, some beast appeared! Healthy, two meters tall. Thugs near his church soaked, and so it is not soaked ... I gave the drape. "
22="Now was on the unexplored world. Saw the lake, near which grazed Electric Chimera. I do not advise going there. "
23="Hello, heroes, your mother! Hare try to beat us with the ATP! If a bitch is not kerf, this is our territory, and horseradish to climb with us! "
24="A group of five people is moving towards the Barrier, supposedly Monolith. Take action.\n\nBarrier\nUnderstood. damn fanatics, so that they ... "
25="Note: If in a village in the dark valley you will be asked to buy some featured rifle for 800 rubles - do not believe it , a scam! "
26="What the hell? At 21.00 starts to trust land, then in the eyes of green and there are zombies! Simply scribe ... And like yesterday, this fortunately has not happened - there have been reports from scientists, Tipo kalayder a broken ... Scribe ... "
27="It is said in the Red Forest, a huge catfish in the river deep. That would look ... "
28="Kruglov - Wheel. Sakharov - Sweet! Ha-ha-ha!\nSakharov\nI'll sell the Artefact, which takes in vital energy. Live your left about ...\nBitch! Creature! Pied ... Communication lost... "
29="NDA ... I'm here thought for one day in the Zone die on average 20 people. And we are here not so much. Although I may be wrong ... "
30="He-he, I drove the customer with the money, leave the link! Already well kurkovatsya, we must do things. "
31="I heard about some lab ... X-16, X-18, X-20 ... Tell the truth or be shot!! "
32="At the bar, one person, a known informant, he sells Transmutation Recipes for Artefacts. Have to go. "
33="Well your mother! In Pripyat is impossible to pass, helicopters beating with all the dope on all living things! "
34="In Limansk, sat down at a construction site Monolith! Gettin outa here before I'm seen! "
35="These are at, drank some vodka, the second day with basin sit ... "
36="Nobody knows who the shooter is? Then one group was interested in them, a lot of money offered. "
37="Snork recently arrived, barely. Discharged both in the head, and he tough that! "
38="Something mutants divorced is living in the woods"
39="Piled a Chimera, just two nests not broken, but we did. "
40="Saw a withered, corpse sucked. Perhaps the nearby den of Bloodsuckers did it to him. "
41="Looking for an experienced mechanic, preferably with knowledge of the device night vision processing is not dusty, pay decent. "
42="On the territory of the ATP found Uazik loaf. Brought. Rode, rode ... So in came a springboard. At the moment, is in space. Out. "
43="Sold exoskeleton condition is excellent, only sealing system is damaged. "
44="Repulsed a major wave of mutants waiting for another one who can help - come. "
45="The warehouse Dolg received brand new FN-2000, much to be in a hurry ... "
46="Damn! E-mine, again full of zombies at Yantar! Neat there, people! \nPotap\nunique information ... "
47="Probe the Bandits, will know how to climb across Batko in hell! "
48="All the STALKERs out of debt: The information on the raid on the mutants and other operations - in a private channel. Not enough yet to leak. "
49="Went to Darkscape looking for Tweed..\nGot chased out by a group of soldiers..  don't know who they were."
50="Is anybody out there?\nI need assistance, anybody?\nWhere the hell am I anyway..."
51="FSS..\nWho the hell is that anyway? Some jerk looking to cause trouble no doubt!"
52="I had it..\nIt was awsome..   but  I  lost it\nit just left my hand and flew away...   can't find it..  gotta find it"
53="Did you hear about F1?\nAll dead, too hot to enter and not a word on what happened!"
54="let's meet at the bar up north, just bring some vodka for the guards at the gate."
55="Tried to go to the old research station..\nBeware, extremely hostile and there is something wrong with that place!"
56="Top end military goods..\nin the Black Market for the next few days."
57="Almost had it back!\nOn the rooftops near the generators but it sliced up some monolith bastards and dissapeared again!"
58="Hey did you hear?\nThe dolg commander in rostok has lost his marbles, sent a team out to find a Panda Bear for him to take to Moscow.."
59="Beware of the Dead Marshes..\nOur whole village has been pushed out by some kind of military assholes!"
60="Need a STALKER, preferably on the side for delicate work, refer to the base ... "
61="There is work to search for equipment, pay by piece, look for me in the unexplored Earth, in the infirmary. "
62="Looking for experienced STALKERs to raid for Artefacts. Since we are owed. Contact Petrenko. "
63="For rare artifact I can download the new firmware, even a satellite channel is not whips. Lanky. "
64="Heh-heh, I drove the money the client is urgently go out on a relationship! "
65="It takes a STALKER, a specialist in combination lock, with the experience of raids north of the Zone. "
66="I heard that the Americans sent us a superhero. It will be interesting to see him. "
67="In the basements do not go there full of creatures! Bypass on top! "
68="Hemul urgently Blow in the bar, it is! "
69="The people! Be careful in the countryside in warehouses - there burning down - piled up on the posts! "
70="STALKERs! Sakharov gives a lot of money for the swag! Still looking for anyone in the X-16 ... I have to send something not risk ... there Fonit wildly, and zombies ... "
71="We need STALKERs for attacks on the Wild Territory. Payment is high. Kruglov.\nLabeled\nHmm ... STALKERs take care of your nerves, do not meet up with this Scientist ... he's a Madman!!! "
72="Recruit into its ranks of experienced trackers, no entrance fees. Zahar. "
73="Bald\nSponge Hop, sports trousers. I'll See - shoot. "
74="We need STALKERs with expertise in deep raids into the Zone. Payment of the corresponding. Interested - knocking in a personal, discuss the meeting place.  "
75="Wolf, answer, talk right., "
76="STALKERs, join Duty!!. Defend the planet from the new plague, which is upon us... "
77="Spam\nMoskvin Coffee - a really, and truly nasty Chinese Coffee!"
78="Spam\nLost weapons, if found return them to me at the old Stardusk wreck in Backwater, come alone!"
79="Spam\nAntizombien - keeps the Zombie in you at bay, even better than Vodka!"
80="Spam\nMoskvin relieves you of constipation in exactly 30 seconds ... no more ... no less ... "

[names]
1=Aleks1970
2=Oleg 
3=Oles 
4=Roma 
5=Ruslan 
6=Sasha 
7=GlowWorm 
8=Slava 
9=LaGator 
10=Jura 
11=Bogdan 
12=Veniamin 
13=Vitaly 
14=Vova 
15=Dima 
16=Ivan 
17=Freischutz 
18=Leche 
19=Andrei 
20=Sanya 
21=aZmoDen 
22=Wadi 
23=Vasyan 
24=Vasek 
25=Vityuha 
26=Vetal 
27=Vovan 
28=Zhorka 
29=Grishka 
30=Michal 
31=Grishko 
32=Dimona 
33=Lech 
34=Dimuha 
35=Mordeth 
36=Fimka 
37=SemtexCyberpunk 
38=Ireland 
39=Mitka 
40=Miha 
41=Mihas 
42=Kolyan 
43=Tolyan 
44=Pavluha 
45=Vesirott 
46=Stepka 
47=Stepuha 
48=Timoha 
49=Felka 
50=Yuras 
51=Yashka 
52=Andrjuxa 
53=Toha 
54=Arkady 
55=Temka 
56=Boryan 
57=Bodya 
58=Andrei 
59=Anton 
60=Oleg 
61=Roman 
62=Alexander 
63=Jammer 
64=Anatoly 
65=Yuri 
66=Bogdan 
67=Veniamin 
68=Vitaly 
69=Vladimir 
70=Dmitri 
71=Ivan 
72=Wolf_Urine 
73=Alexey 
74=Sane 
75=Sanya 
76=Arthur 
77=Yashka 
78=Yarick 
79=Yara 
80=Slava 
81=Zaldron 
82=Borka 
83=Bogdan 
84=Slawik 
85=Vadim 
86=Wadi 
87=Vadik 
88=Roller 
89=Valera 
90=Schurick 
91=Vase 
92=Vaska 
93=Vasko 
94=Vienna 
95=Whyte 
96=Vitka 
97=Vitalik 
98=Vlad 
99=Vova 
100=Vovka 
101=Leni 
102=Seva 
103=Sevco 
104=Gena 
105=Lord_Santa 
106=George 
107=Gosh 
108=Jore 
109=RemCNelly 
110=Gleb 
111=Grisha 
112=Alex 
113=Grishka 
114=Grishko 
115=Auzymindias 
116=Danilo 
117=Danko 
118=Denis 
119=Dima 
120=Dimka 
121=Dmytro 
122=Jack 
123=Leszka 
124=Zhenka 
125=Egor 
126=Egorka 
127=aZmoDen 
128=Vanya 
129=Vanka 
130=Igorek 
131=Ilya 
132=Kostya 
133=Kostik 
134=Death_Eagle 
135=Lew 
136=Leni 
137=Lenka 
138=Grimwald 
139=Matvey 
140=Mite 
141=Misha 
142=Mishka 
143=Nikita 
144=Nik 
145=Anton 
146=Kolya 
147=Oleg 
148=Pasha 
149=Pashka 
150=Petro 
151=Petey 
152=Petka 
153=Roma 
154=Romka 
155=Rostik 
156=Toshka 
157=Rus 
158=Sawa 
159=Semen 
160=Sema 
161=Serega 
162=Twilight2k 
163=Stepan 
164=dAVROs 
165=Pilgrim 
166=Timka 
167=Arte 
168=Fedora 
169=Fedya 
170=Fedka 
171=File 
172=Filka 
173=Edik 
174=Yurka 
175=Eureka 
176=Yurko 
177=Yash 
178=Sivy 
179=Mad 
180=Rotten 
181=TB3D 
182=spy 
183=Bizon 
184=Bober 
185=Bulldog 
186=Bic 
187=Sparrow 
188=Dyatel 
189=beast 
190=Serpent 
191=Hunchback 
192=Boar 
193=Karas 
194=Kenar 
195=Bedbug 
196=Bacon 
197=Los 
198=Patsyuk 
199=Udav 
200=Baton 
201=Bity 
202=Long 
203=Bespredel 
204=Bolt 
205=Brzytwa 
206=Tambourine 
207=Valet 
208=Vint 
209=Dynamite 
210=Kozyr 
211=Brass_knuckles 
212=Kosyak 
213=Dohly 
214=Crest 
215=Kryuk 
216=Lapot 
217=Lom 
218=Panadol 
219=Perot 
220=Piston 
221=Pyatak 
222=Reszka 
223=Death 
224=Dohodyaga 
225=Tochilo 
226=Ace 
227=Chekan 
228=Tempo 
229=Shiloh 
230=Szpala 
231=Hell 
232=Shuher 
233=fist 
234=Skull 
235=Dohlyak 
236=Barmaley 
237=Baty 
238=Undead 
239=Rambo 
240=Susanin 
241=Terminator 
242=Chapay 
243=Chingiz 
244=Banana 
245=Baton 
246=Inside 
247=Bata 
248=Bayan 
249=Bratan 
250=Gangrene 
251=Gluck 
252=Gradus 
253=Spirit 
254=Zvezdets 
255=Izgoj 
256=Brass_knuckles 
257=Zhzheny 
258=Kozyr 
259=Kosyak 
260=Lapot 
261=Leshy 
262=Mawr 
263=Nishtjak 
264=Oblom 
265=Erick 
266=Pepper 
267=Rashpil 
268=Zhirdyay 
269=Suhar 
270=Upyr 
271=Zhlob 
272=Bity 
273=Zhmot 
274=Jmour 
275=Izverg 
276=Caleca 
277=Kolotun 
278=Cosi 
279=Krivoy 
280=AQ 
281=Bald 
282=Lyuty 
283=Blatnoj 
284=Local 
285=Mutny 
286=Myaty 
287=Odnoglazy 
288=Padla 
289=Parasite 
290=Cool 
291=Swine 
292=churned 
293=Psycho 
294=Dino 
295=Rvany 
296=Rvach 
297=Blind 
298=Soplya 
299=Stilyaga 
300=Metropolitan 