;<!-- TB3D 1.0.20e -->
[dead_reason]
1="a Springboard"
2="a Burner"
3="a Vortex"
4="a Whirligig"
5="an Elektra"
6="of Shrapnel wounds ... the poor bastard didn't even see it coming."
7="a Wild Boar"
8="a Dog"
9="a Pseudo-dog"
10="a Bloodsucker"
11="some Rats"
12="It's not clear exactly what happened ... but, he's dead."
13="Looks like a radiation burn"
14="Ripped to shreds, do not know what kind of creature did it"
15="Shot in the head"
16="Had a hand ripped off in an Anomaly. Died because of blood loss"
17="His feet are a terrible mess ... must have wandered into a Fruit Punch anomaly"
18="Shot in the chest"
19="Shot in the heart and in the head - a professional job. Most likely Mercenaries ..."
20="A bloody smear on the concrete ... torn scraps of a shredded suit, broken PDA. must have ..."
21="Something must have been chasing him. He ran straight into an Anomaly"
22="Bleeding from the nose, and ears ... Looks like radiation poisoning"
23="No visible wounds .. an unexplained death"
24="Fell into a Burner Anomaly. Shortly before this, he must have dropped his PDA, so I can not identify him"
25="Splattered all over the place .. a typical Whirligig death"
26="He didn't even know what he was carrying in his backpack. Died from highly radioactive artefacts"
27="The suit is intact, but inside, it's a mess. I don't know what the hell happened"
28="Marauders"
29="Ran into some Marauders ... didn't stand a chance"
30="Shot in the leg. Could not make it to safety, died of blood loss"
31="Shot in the chest - put a hole right through him ..."
32="Died from radiation poisoning ... should have been more careful"
33="The body has been partially eaten. Most likely by dogs .. poor bastard"
34="Was gone without a trace ... only his destroyed, burnt PDA found behind a boulder ..."
35="His leg was ripped apart straight to the bone, died from a blood hemorrhage"
36="Had a serious fracture. Couldn't move, lay there in pain for hours ... Something must have found him ..."
37="Shot at point-blank range. I must have been an ambush of Marauders ... filthy bastards!!"
38="A shot in the back of the head"
39="I noticed a Bloodsucker lurching over the body. When I killed the creature, and approached ... he was already dead"
40="Strange burns cover the body. Nothing like the Burner anomaly.."
41="A laceration on the chest. I don't know exactly what happened .. shit."
42="I found a PDA next to the body. I don't know why, but the dictaphone was switched on. All it recorded was hours of endless screaming. Horrible."
43="Found a body .. all cut to pieces. Beside it, there was a small knife. What the hell is going on?!"
44="A skeleton ... wearing unscathed S.T.A.L.K.E.R. gear .. WTF?!"
45="Gnawed to the bone by Rats .."
46="Both arms are broken and his neck is twisted. Who did this?!"
47="A punctured skull ... must have been a Sniper ..."
48="Stitched up shoulder. No bandages, Died from infection ..."
49="came a pack of mad dogs."
50="came a pack of mad Pseudodogs."
51="a Controller appeared, shit. Who's next, beware!"
52="came a Controller."
53="Military Helicopter ... Probably a raid ..."
54="there was a wave of mutants, barely got out alive! other was not so lucky."
55="attacked by mutants."
56="saw a mangled corpse there. Did not bother to investigate, perhaps, there is an anomaly there somewhere ..."
57="saw a rotting corpse nearby. Perhaps there is a lair of Bloodsuckers in the vicinity ..."
58="heard a terrible scream. Damn, I'm not going near there again!!! ..."
59="saw a bloody S.T.A.L.K.E.R. being dragged along the ground by a Bloodsucker ... fuck!!!"
60="saw a pack of dogs, dragging a S.T.A.L.K.E.R. into the bushes. I think he was still alive!!!"
61="was involved in a fiery exchange with some Bandits. We killed all of them. Dumb Fucks!!! "
62="ran into a Military patrol, killed them all. Avoid that area if you can. There is sure to be a raid now!!"
63="caught by a Military patrol. Had to shoot them all. I would get out of here if I were you ..."
64="a savage Snork killed a S.T.A.L.K.E.R. here. Damn, how many of those fucking things are there, anyways?!"
65="there are a lot of strange new Anomalies around here. Beware S.T.A.L.K.E.R.!!!"

[where_dead]
1="in the Cordon"
2="in the Cordon, near the tunnel with an Elektra"
3="in the Cordon, near the collapsed bridge"
4="in the Cordon, beside some rusty locomotive"
5="around the Cordon"
6="close to the Cordon"
7="before the Cordon"
8="far from the Cordon"
9="next to the Cordon"
10="near the Cordon"
11="at the Dump"
12="at the Dump, near the hangar"
13="around the Dump"
14="in the vicinity of the Dump"
15="before the Dump"
16="far from the Dump"
17="next to the Dump"
18="near the Dump"
19="in Agroprom"
20="in Agroprom, near the Institute"
21="around Agroprom"
22="in the vicinity of Agroprom"
23="before Agroprom"
24="far from Agroprom"
25="next to Agroprom"
26="near Agroprom"
27="in Yantar"
28="in Yantar, in the swamp"
29="in Yantar, at the factory"
30="around Yantar"
31="close to Yantar"
32="in front of Yantar"
33="near Yantar"
34="next to Yantar"
35="near Yantar"
36="in the Dark Valley"
37="around the Dark Valley"
38="close to the Dark Valley"
39="before the Dark Valley"
40="not far from the Dark Valley"
41="next to the Dark Valley"
42="near the Dark Valley"
43="at the Army Warehouses"
44="around the Army Warehouses"
45="close to the Army Warehouses"
46="before the Army Warehouses"
47="not far from the Army Warehouses"
48="next to the Army Warehouses"
49="near the Army Warehouses"
50="near the abandoned village"
51="near the deserted village"
52="in front of an abandoned village"
53="near the deserted village"
54="next to an abandoned village"
55="near the deserted village"
56="near the water tower, in the deserted village"
57="before the water tower in the village"
58="near the water tower, in the deserted village"
59="next to the old water tower"
60="near the water tower, in the village"
61="in the vicinity of the Bar"
62="before the Bar"
63="near the Bar"
64="near the Barrier"
65="near the Barrier"
66="before the Barrier"
67="near the Barrier"
68="next to the Barrier"
69="near the Barrier"
70="Rostock factory"
71="around the Rostock plant"
72="in the vicinity of the Rostock plant"
73="the Rostock plant"
74="not far from the Rostock plant"
75="next to the Rostock plant"
76="near the Rostock plant"
77="near the Duty base"
78="near the Duty checkpoint"
79="before the Duty checkpoint"
80="far from the Duty checkpoint"
81="next to the Duty checkpoint"
82="near the Duty checkpoint"
83="near the entrance to the Freedom base"
84="near the Freedom base"
85="next to the Freedom base"
86="near the Freedom base"
87="near the entrance to the Freedom base"
88="near the Freedom base"
89="in the ATP"
90="around the ATP"
91="in the vicinity of the ATP"
92="before the ATP"
93="far from the ATP"
94="next to the ATP"
95="near the ATP"
96="Farm"
97="near the farm"
98="in the vicinity of the farm"
99="in front of the farm"
100="not far from the farm"
101="next to the farm"
102="near the farm"
103="around the Scientists' camp"
104="near the Scientists' camp"
105="not far from the Scientists' camp"
106="next to the Scientists' camp"
107="near the entrance to the factory building in Yantar"
108="near the Yantar factory gates"
 